Crop adaptation through gene flow

### 2016-06-29 crop_adaptation_gene_flow_gj_outline.tex
Update crop_adaptation_gene_flow_gj_outline.tex

\subsection*{Cotton}
wendel1989genetic:
bidirectinal gene flow between diploid species G. arboreum and G. herbaceum
independent domestication events of G. arboreum and G. herbaceum

@@

Cotton tolerates crosses quite well.

>>>>

\subsection*{Cotton}

Gossypium hirsutum is the most important and most agronomically grown cotton today.
G. hirsutum is from Mexico.
There are many species in the genus, from around the world, and many have been cultivated.

percy1990allozyme:
G. barbadense is grown commercially in S. America, where it hybridizes with G. hirsutum as well

wendel1989genetic:
bidirectinal gene flow between diploid species G. arboreum and G. herbaceum
independent domestication events of G. arboreum and G. herbaceum

@@

Cotton readily tolerates interspecific crossing.
This leads to a reticulated phylogeny.
